---
title       : Forecast - GDP per capita 
subtitle    : 
author      : aadami
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Summary


. In this project, we use historical data for GDP per capita obtained from the World Bank website (http://databank.worldbank.org/data/reports.aspx?source=world-development-indicators). Using these data, which cover the period from 1960 to 2014, we made the forecast of the period from 2015 to 2020, applying the 'forecast' package available in R software.

. The method was implemented and shared through a Web application, available at https://albertoadami71.shinyapps.io/FORECASTGDP.




--- .class #id 

## Method

We illustrate our method using the data of the Brazilian GDP per capita, expressed in current US$. Thus, we have the following vector 'brazil_gdp':

```{r, echo=FALSE}
brazil_gdp = c(209.1988, 203.9552, 258.7577, 290.0583, 259.4670, 259.0042, 312.8819, 344.2945, 371.3931, 400.2629, 440.9931, 500.0341, 580.4885, 767.3099, 993.2896, 1140.9011, 1374.5358, 1548.3983, 1723.1372, 1885.0911, 1923.2826,  2106.6790, 2199.7020, 1551.7730, 1560.4558, 1629.2649, 1919.8648, 2064.6540, 2276.2406, 2879.4999, 3071.6280, 2663.7864, 2513.6379, 2777.3482, 3482.5298, 4827.3276, 5163.2658, 5279.1505, 5083.6265, 3476.0808, 3738.7194, 3136.4967, 2810.2308, 3044.2550, 3597.9788, 4733.1835, 5809.1179, 7241.0790, 8700.6133, 8462.3891, 11124.0769, 13042.1977, 11922.7047, 11711.0633, 11384.6181)
print(brazil_gdp)


```


--- .class #id 

In the sequel we apply the exponential smoothing state space model (ets) to calculate the GDP predictions for the next six years (2015-2020).


```{r, echo=TRUE, results='asis'}
library(forecast)
tsbr = ts(brazil_gdp)
etsbr =ets(tsbr,model="AAN")
fcast = forecast(etsbr,h=6) 
print(fcast$mean)

```

--- .class #id 

Finally, we plot a graphic with historical data (blue) followed by the forecasts (grey). 

```{r, echo=FALSE, results='asis', fig.height=6, fig.width=12}
x = seq(from=1960, to=2014, by=1)
prev = c(tsbr[length(tsbr)-1],as.vector(fcast$mean))
anos=c(2014,2015,2016,2017,2018,2019,2020)
xaux=c(x,anos)
xmin = min(xaux)
xmax = max(xaux)
ymin = min(min(tsbr[!is.na(tsbr)]),min(prev))
ymax = max(max(tsbr[!is.na(tsbr)]),max(prev))
plot(x,tsbr,type="l", col = "blue",xlim=c(xmin,xmax),ylim=c(ymin,ymax),xlab="year",ylab="GDP per capita (current US$)", main = "Brazil: GDP per capita")
par(lwd=3)
lines(anos,prev,col="grey")


```
Conclusion: In this work, we found that the R software, besides being an excellent tool for data analysis, also allows the sharing of Web applications and the preparation of presentation slides.
